\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-14 paper.tex
Revise wording

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.

@@

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the streaming data from data providers.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks since brokers are expected to have higher resource. Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel. For each product, brokerage fees will be charged by the broker.

@@

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. With every participant in data marketplace registers on TangleID, one can easily verify data providers' identity to ensure the data persistency from data sources.

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

\subsubsection{Blind Signature}
 It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of MAM channel to smart contract without knowing it.

\subsubsection{IPFS}
Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users. In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to IPFS in order to provide users with search capabilities to meet the consumers' need.

>>>>

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to post participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.

@@

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a significant challenge for most consumers to collect the desired data by themselves. So they look to purchasing the streaming data from data providers.

\subsubsection{Broker}
Brokers represent data providers and consumers to perform computing tasks as brokers are expected to have higher resource. Some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Once a qualified data provider requests to launch a new product, the broker is requested to deal with the trading process and publish the provider’s data streams to the MAM channel. Brokerage fees for each product will be charged by the broker.

@@

\subsubsection{TangleID}
The TangleID\cite{TangleID} is a self-sovereign identity system based on IOTA that do not require any third-party authority to verify an identity and its digital footprint. With TangleID, the digital footprint is converted into digital assets under the principle of Decentralized Identifiers (DIDs)\cite{DID} defined by W3C. Posting DID documents on MAM makes TangleID a GDPR-Complianced system. Every participant in the data marketplace registers on TangleID, hence one can easily verify data providers' identity to ensure the data persistency from data sources.

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. The code in the smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

\subsubsection{Blind Signature}
 It is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Blind signature\cite{blindSig} is a form of digital signature where the message is first "blinded" by a random "blinding factor", then passed to a signer to sign. The resulting message, along with the blinding factor, can be later verified with the signer's public key. In our system design, brokers would perform blind signature during the process of adding new products for data providers, in order to send the secret key of the MAM channel to smart contract without knowing it.

\subsubsection{IPFS}
Inter-Planetary File system(IPFS)\cite{IPFS} is a peer-to-peer network for storing and accessing files, websites, applications, and data in a distributed file system which is not maintained with certain nodes or entities but all IPFS users. In our proposed architecture, brokers are responsible to publish the metadata of products, including title, data provider information and data preview to the IPFS in order to provide users with search capabilities to meet the consumers' need.
